%-------------------------
% Dishant Shah — Resume
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{geometry}

\geometry{left=0.6in, right=0.6in, top=0.5in, bottom=0.5in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

\setlength{\footskip}{4.08pt}

%-------------------------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
  {\Huge \textbf{Dishant Shah}} \\[4pt]
  \small
  San Jose, CA $\mid$
  \href{mailto:dshah9542@gmail.com}{dshah9542@gmail.com} $\mid$
  256-604-9611 $\mid$
  \href{https://linkedin.com/in/dishantk-shah}{linkedin.com/in/dishantk-shah} $\mid$
  \href{https://github.com/Dishant-Shah-Projects}{github.com/Dishant-Shah-Projects}
\end{center}

%---------- SUMMARY ----------
\vspace{2pt}
\small{Software engineer with 4+ years building and scaling enterprise SaaS systems at Intapp, with a focus on backend services and cloud infrastructure. Led a full AWS-to-Azure migration consolidating 30 microservices onto AKS, delivered performance improvements reducing API latency by up to 97\%, and owned the full DevOps lifecycle from Jenkins pipelines to Argo CD and Helm. Currently building agentic development tooling for sustained AI-assisted engineering workflows.}
\vspace{2pt}

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Software Engineer}{August 2021 -- Present}
    {Intapp --- Palo Alto, CA}{Cloud-based SaaS platform for professional services firms (legal, accounting, finance)}
  \resumeItemListStart
    \resumeItem{Engineered backend services across three domains within the consolidated mini-monolith architecture: data processing pipelines, frontend-facing APIs, and system management --- serving as the core application layer in both AWS and Azure environments.}
    \resumeItem{Led migration from AWS microservices to Azure AKS, consolidating 30 microservices into 3 mini-monolith Docker images --- reducing operational overhead and network latency across service boundaries.}
    \resumeItem{Implemented a caching layer for mostly-static data, reducing API response times from $\sim$2 minutes to $\sim$3 seconds ($\sim$97\% improvement) by eliminating redundant database round trips.}
    \resumeItem{Proposed and executed architecture refinements to eliminate unnecessary network hops between services, reducing end-to-end update times from 30 seconds--several minutes to under 2 seconds.}
    \resumeItem{Refactored database schema to remove redundant tables and simplify complex queries, improving query performance and long-term maintainability.}
    \resumeItem{Designed and built an SMTP email delivery server from scratch using Node.js, enabling transactional and notification email workflows within the product.}
    \resumeItem{Maintained, debugged, and enhanced data delivery pipelines surfacing backend data to frontend consumers --- migrating from real-time Kafka in AWS to batch polling in Azure to reduce operational complexity.}
    \resumeItem{Built monitoring dashboards in Grafana/Prometheus and automated test suites to ensure observability and reliability during and after the cloud migration.}
    \resumeItem{Managed cloud infrastructure across AWS (Lambda, CloudFormation, Terraform) and Azure (AKS, Argo CD, Helm charts) via Jenkins CI/CD pipelines.}
    \resumeItem{Designed and built CI/CD pipelines for PySpark data applications migrated from Databricks to AKS, enabling automated testing and deployment of data workflows.}
  \resumeItemListEnd

  \resumeSubheading
    {Student Researcher / Researcher I}{January 2015 -- August 2019}
    {Biomedical Engineering, University of Alabama at Birmingham}{}
  \resumeItemListStart
    \resumeItem{Published 3 peer-reviewed papers and presented at 3 national conferences on NO-releasing nanomatrix gel research for dental regeneration and islet transplantation.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Agentic Development Platform} $\mid$ \textit{Python, FastAPI, Docker, SQLite, GitHub API, Claude Code, MCP, Bash}}{2025}
  \resumeItemListStart
    \resumeItem{Designed and deployed a self-hosted agentic development platform with two components: a language-agnostic scaffold defining a 9-stage structured workflow with 10 agent profiles and 11 reusable skills; and an autonomous runner server that polls GitHub issues, spawns Docker containers executing Claude Code agents, and manages 3 concurrent workers on a Proxmox VM.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Algorithmic Trading Bot} $\mid$ \textit{Python, alpaca-py, systemd}}{2025 --- In progress}
  \resumeItemListStart
    \resumeItem{Personal-scale project built entirely using the Agentic Development Platform above. A long-only algorithmic trading system with a multi-symbol backtesting engine, SMA(50/200) trend strategy, ATR-based risk sizing, and portfolio heat enforcement. Features walk-forward validation, health/readiness HTTP endpoints, JSON logging with webhook alerts, and systemd deployment.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{FlavorNation} $\mid$ \textit{Go, Gin, Next.js 15, React 19, TypeScript, Tailwind CSS, MongoDB, Docker}}{2024 -- 2025}
  \resumeItemListStart
    \resumeItem{Built a full-stack restaurant discovery platform for Diners, Drive-Ins and Dives, including a custom scraper to collect all episodes and restaurants, a Go/Gin REST backend with MongoDB, and a Next.js 15 + React 19 frontend. Deployed via Docker on a self-hosted Proxmox VM with Docker Compose and health check endpoints.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Discord Social Credit Bot} $\mid$ \textit{TypeScript, Node.js, Discord.js v14, Sequelize, SQLite, Vitest, Docker}}{2024 -- 2025}
  \resumeItemListStart
    \resumeItem{Designed and deployed a Discord bot implementing a social credit system with emoji-based reward/penalty mechanics and leaderboards. Built with repository pattern, structured logging via Pino, type-safe command framework, database migrations, and comprehensive test coverage. Deployed on Proxmox via Docker.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Graduate Academic Projects} $\mid$ \textit{Node.js, React.js, Express.js, MongoDB, MySQL, Redis, Kafka, GraphQL}}{2020 -- 2021}
  \resumeItemListStart
    \resumeItem{Built full-stack MERN prototypes (Glassdoor, Yelp) with Redis caching ($\sim$95\% latency reduction), Kafka-backed API queues, AWS load balancing (configured for 10K concurrent users), and JWT authentication.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- SKILLS ----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
    \textbf{Languages:} JavaScript, TypeScript, Python, Go, Java, C\# \\[2pt]
    \textbf{Backend:} Node.js, Express.js, .NET, Gin, RESTful APIs, GraphQL, Microservices, PySpark \\[2pt]
    \textbf{Frontend / Mobile:} React.js, Next.js, React Native, Redux, HTML, CSS \\[2pt]
    \textbf{Databases:} PostgreSQL, DynamoDB, MongoDB, MySQL, Redis, SQLite \\[2pt]
    \textbf{Cloud \& Infrastructure:} Azure (AKS, Key Vault, Blob Storage), AWS (S3, DynamoDB, SQS, Lambda), Docker, Kubernetes, Kafka, Databricks \\[2pt]
    \textbf{DevOps \& Observability:} Jenkins, Argo CD, Helm, Terraform, CloudFormation, Grafana, Prometheus, Git \\[2pt]
    \textbf{AI Tooling:} Claude Code, MCP, Agentic Scaffolding, Multi-agent Orchestration, Prompt Engineering \\[2pt]
    \textbf{Practices:} TDD, Agile, Event-Driven Architecture, Repository Pattern, Domain-Driven Design
  }}
\end{itemize}

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {San Jose State University}{San Jose, CA}
    {Master of Science in Software Engineering}{May 2022}

  \resumeSubheading
    {University of Alabama at Birmingham}{Birmingham, AL}
    {B.S. Biomedical Engineering, Minor: Computer Science, Chemistry}{August 2018}
  \resumeItemListStart
    \resumeItem{Presidential Scholarship, Dean's List, Honors College, BMES Travel Award, 1st Place Fall Undergraduate Research Expo}
    \resumeItem{Published 3 peer-reviewed papers (Journal of Clinical Medicine 2020, ACS Biomaterials 2017, Nano Convergence 2016)}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
